Soybean herbicide study - Dan Smith

### 2021-09-14 soyherb.Rmd
Update soyherb.Rmd
as

@@

```{r fig.align='center'}
ggplot(data, aes(x=reorder(other,waterhempcontrol_14), y=waterhempcontrol_14,
       fill=trade, color=trade)) +
  geom_boxplot(color="black") +
  geom_jitter(alpha=0.2) +
  facet_grid(year ~ location) +
  coord_flip() +
  labs(x="", y="Waterhemp control (%)") +
  theme_minimal() +
  theme(legend.position = "none")
```

@@

```{r fig.align='center'}
ggplot(data, aes(x=reorder(other,waterhempcontrol_28), y=waterhempcontrol_28,
       fill=trade, color=trade)) +
  geom_boxplot(color="black") +
  geom_jitter(alpha=0.2) +
  facet_grid(year ~ location) +
  coord_flip() +
  labs(x="", y="Waterhemp control (%)") +
  theme_minimal() +
  theme(legend.position = "none")
```

@@

```{r fig.align='center', message=FALSE, warning=FALSE}
ggplot(data, aes(x=reorder(other,waterhempcontrol_harvest), y=waterhempcontrol_harvest,
       fill=trade, color=trade)) +
  geom_boxplot(color="black") +
  geom_jitter(alpha=0.2) +
  facet_grid(year ~ location) +
  coord_flip() +
  labs(x="", y="Waterhemp control (%)") +
  theme_minimal() +
  theme(legend.position = "none")
```

@@

```{r fig.align='center', message=FALSE, warning=FALSE}
ggplot(data, aes(x=reorder(other,biomass_gm2), y=biomass_gm2,
       fill=trade, color=trade)) +
  geom_boxplot(color="black") +
  geom_jitter(alpha=0.2) +
  facet_grid(year ~ location) +
  coord_flip() +
  labs(x="", y="Weed biomass (g m2)") +
  theme_minimal() +
  theme(legend.position = "none")
```

@@

```{r fig.align='center'}
plot(lsmeans_14, ~ herbicide, comparisons=TRUE, type="response", alpha=0.05, adjust="none")
```

```{r message=FALSE, warning =FALSE}
CLD(lsmeans_14$emmeans, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>%
  kbl() %>%
  kable_classic_2(full_width = F)
```

@@

```{r fig.align='center'}
plot(lsmeans_28, ~ herbicide, comparisons=TRUE, type="response", alpha=0.05, adjust="none")
```

@@

```{r message=FALSE, warning =FALSE}
CLD(lsmeans_28$emmeans, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>%
  kbl() %>%
  kable_classic_2(full_width = F)
```

@@

@@

```{r message=FALSE, warning =FALSE}
CLD(lsmeans_fit$emmeans, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>%
  kbl() %>%
  kable_classic_2(full_width = F)
```

>>>>

```{r}
view(data)
```

@@

```{r fig.align='center'}
ggplot(data, aes(x = reorder(other,waterhempcontrol_14), 
                 y = waterhempcontrol_14,
       fill=trade, color=trade)) +
  geom_boxplot(color="black") +
  geom_jitter(alpha=0.2) +
  facet_grid(year ~ location) +
  coord_flip() +
  ylim(0, 100) +
  labs(x="", y="Waterhemp control (%)") +
  theme_minimal() +
  theme(legend.position = "none")
```

@@

```{r fig.align='center'}
ggplot(data, aes(x=reorder(other,waterhempcontrol_28), y=waterhempcontrol_28,
       fill=trade, color=trade)) +
  geom_boxplot(color="black") +
  geom_jitter(alpha=0.2) +
  facet_grid(year ~ location) +
  coord_flip() +
  ylim(0, 100) +
  labs(x="", y="Waterhemp control (%)") +
  theme_minimal() +
  theme(legend.position = "none")
```

@@

```{r fig.align='center', message=FALSE, warning=FALSE}
ggplot(data, aes(x=reorder(other,waterhempcontrol_harvest), y=waterhempcontrol_harvest,
       fill=trade, color=trade)) +
  geom_boxplot(color="black") +
  geom_jitter(alpha=0.2) +
  facet_grid(year ~ location) +
  coord_flip() +
  ylim(0, 100) +
  labs(x="", y="Waterhemp control (%)") +
  theme_minimal() +
  theme(legend.position = "none")
```

@@

```{r fig.align='center', message=FALSE, warning=FALSE}
ggplot(data, aes(x=reorder(other,biomass_gm2), y=biomass_gm2,
       fill=trade, color=trade)) +
  geom_boxplot(color="black") +
  geom_jitter(alpha=0.2) +
  facet_grid(year ~ location) +
  coord_flip() +
  ylim(0, 100) +
  labs(x="", y="Weed biomass (g m2)") +
  theme_minimal() +
  theme(legend.position = "none")
```

@@

```{r fig.align='center'}
plot(lsmeans_14, ~ herbicide, comparisons=TRUE, type="response", 
     alpha=0.05, adjust="none") + xlim(0, 1)
```

```{r message=FALSE, warning =FALSE}
multcomp::cld(lsmeans_14$emmeans, alpha=0.05, Letters=letters, 
    adjust="none", 
    reversed = TRUE) %>%
  kbl() %>%
  kable_classic_2(full_width = F)
```

@@

```{r fig.align='center'}
plot(lsmeans_28, ~ herbicide, comparisons=TRUE, type="response", 
     alpha=0.05, adjust="none") + xlim(0,1)
```

@@

```{r message=FALSE, warning =FALSE}
multcomp::cld(lsmeans_28$emmeans, alpha=0.05, Letters=letters, 
    adjust="none", reversed = TRUE) %>%
  kbl() %>%
  kable_classic_2(full_width = F)
```

@@

```{r}
nd14 <- data.frame(lsmeans_14$emmeans) %>% 
  mutate(dat = "14 DAT")
nd28 <- data.frame(lsmeans_28$emmeans)  %>% 
  mutate(dat = "28 DAT")
nd <- bind_rows(nd14, nd28)

nd %>% 
  mutate(herbicide = fct_relevel(herbicide, c("PRE fb glufosinate",
                    "PRE fb glufosinate + acetochlor",
                    "PRE fb glufosinate + dimethenamid-P",
                    "PRE fb glufosinate + S-metolachlor",
                    "PRE fb glufosinate + imazethapyr",
                    "PRE fb glufosinate + fomesafen",
                    "PRE fb glufosinate + pyroxasulfone",
                    "PRE fb glufosinate + fomesafen + acetochlor",
                    "PRE fb glufosinate + fomesafen + S-metolachlor"))) %>%
ggplot(aes(x=herbicide, response, y=response*100)) + 
  facet_wrap(~dat) +
  coord_flip() + 
  geom_point(size=3, color="#282728") + 
  theme_bw() +  
  labs(y="Waterhemp control (%)", x="", title="") +
  geom_errorbar(aes(ymin  =  lower.CL*100, ymax  =  upper.CL*100), width =  0.3, size  =  1, color="#282728") + 
  theme(axis.title = element_text(size=20, color="#282728", face="bold"), 
        axis.text.x = element_text(size=18, angle=0, hjust=1,
                                   color="#282728"), 
        axis.text.y = element_text(size=18, color="#282728"),
        plot.title = element_text(size=30, face="bold", hjust = 1, 
                                    color="#c5050c"), 
        strip.text = element_text(size=25, face="bold", color="#282728"),          strip.background =element_rect(fill="#dadfe1")) + 
  geom_hline(yintercept=90, linetype="dashed", color="#c5050c", size=1.2, show.legend = TRUE) +
  ylim(0,100)

ggsave("figures/Figure2.png", width=18, height=9, dpi=600)
```

@@

```{r message=FALSE, warning =FALSE}
multcomp::cld(lsmeans_fit$emmeans, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>%
  kbl() %>%
  kable_classic_2(full_width = F)
```
